### 2016-12-17 doc/paper/paper.tex
described Genetic Algorithm

\begin{algorithm}[!t]
  \caption{Genetic Phase}
  \label{alg.gen}
  \algsetup{linenosize=\tiny}
  \scriptsize
  \DontPrintSemicolon
  \SetAlgoVlined
  \SetKwInOut{Input}{Input}
  \SetKwInOut{Output}{Output}
  \SetKwInOut{Require}{Require}
  \SetKwProg{Fn}{Function}{}{}
  \Input{
    $b_N$ is target branch, $cfg$ is control-flow graph\\
    $cinfo$ is constant info, $config$ is configuration file\\
    $ifun$ instrumented JS function, $sig$ type signature
  }
  \Output{
     element $p^*$ on which the best fitness $f^*$ is achieved  
  }
  \Fn{$Genetic(b_N, cfg, cinfo, config, ifun, sig)$}{
    $(size_P, size_A, size_G, rate_C, rate_M) \longleftarrow Read(config)$\label{alg.gen.read.config}\;
    $archive \longleftarrow \emptyset$; $i \longleftarrow 0 $\label{alg.gen.arch.init}\;
    $pop \longleftarrow Random(cinfo, size_P)$\label{alg.gen.random.gen}\;
    \Repeat{$isPerfect(f^*) \vee i > size_G $}{\label{alg.gen.loop.begin}
      $scoredPop \longleftarrow \emptyset$\;
      \ForAll{$p \in pop$}{
        $args \longleftarrow MakeArguments(p, sig)$\;
        $(tr, d_B, d_L, consts) \longleftarrow ifun(args)$\;
        $(f, p) \longleftarrow Evaluate(b_N, cfg, tr, d_B, d_L)$\;
        $scoredPop \longleftarrow (f, p) \cup scoredPop$\;
        $cinfo \longleftarrow consts \cup cinfo$\;
      }
      $combo \longleftarrow scoredPop \cup archive$\;
      $cross \longleftarrow Crossover(combo, rate_C)$\;
      $mut \longleftarrow Mutation(combo, cinfo, rate_M)$\;
      $pop \longleftarrow cross \cup mut$\;
      $archive \longleftarrow GetBest(combo, size_A)$\;
      $(f^*, p^*) \longleftarrow head(archive)$\;
      $i \longleftarrow i + 1$\;
    }\label{alg.gen.loop.end}
    \Return{$(f^*, p^*)$} 
  }
\end{algorithm}

The heart of our test data generation framework is in the \emph{Genetic Phase}. The main workflow of the underlying genetic algorithm (GA) is quite standard~\cite{poli2008field}, and with some adaptations presented in Algorithm~\ref{alg.gen}. We start with the reading of the \emph{config} file in line~\ref{alg.gen.read.config}. As a result we get information about the number of elements in a population ($size_P$), size of the archive ($size_A$), number of generations ($size_G$) and respectively crossover ($rate_C$) and mutation ($rate_M$) rates. \emph{Archive} has the size of  $size_A$ and stores the most fitted candidates observed so far. It is empty in the beginning of the evolution (line~\ref{alg.gen.arch.init}). First population of $size_P$ is randomly generated (line~\ref{alg.gen.random.gen}) based on the values passed through the \emph{cinfo}. Inside of the loop (lines~\ref{alg.gen.loop.begin}-\ref{alg.gen.loop.end}) we are trying optimize the ....

Then, this population is evaluated against given fitness function. If the perfectly fitted candidate is found or the budget is exhausted, the algorithm terminates and reports the best candidate so far. Otherwise it enters an iterative phase where after a selections procedure some candidates are crossed over and others are mutated. Afterwards a new population is formed and the evaluation repeats.

@@

@@

\subsection{Static Analysis of JavaScript}
\label{sub.sec.js.static.anal}

@@

@@

@@

>>>>

\begin{algorithm}[!t]
  \caption{Genetic Phase}
  \label{alg.gen}
  \algsetup{linenosize=\tiny}
  \scriptsize
  \DontPrintSemicolon
  \SetAlgoVlined
  \SetKwInOut{Input}{Input}
  \SetKwInOut{Output}{Output}
  \SetKwInOut{Require}{Require}
  \SetKwProg{Fn}{Function}{}{}
  \Input{
    $b_N$ is target branch, $cfg$ is control-flow graph\\
    $cinfo$ is constant info, $config$ is configuration file\\
    $ifun$ instrumented JS function, $sig$ type signature
  }
  \Output{
     element $p^*$ on which the best fitness $f^*$ is achieved  
  }
  \Fn{$Genetic(b_N, cfg, cinfo, config, ifun, sig)$}{
    $(size_P, size_A, size_G, rate_C, rate_M) \longleftarrow Read(config)$\label{alg.gen.read.config}\;
    $archive \longleftarrow \emptyset$; $i \longleftarrow 0 $\label{alg.gen.arch.init}\;
    $pop \longleftarrow Random(cinfo, size_P)$\label{alg.gen.random.gen}\;
    \Repeat{$isPerfect(f^*) \vee i > size_G $}{\label{alg.gen.loop.begin}
      $scoredPop \longleftarrow \emptyset$\;
      \ForAll{$p \in pop$}{\label{alg.gen.eval.begin}
        $args \longleftarrow MakeArguments(p, sig)$\label{alg.gen.make.args}\;
        $(tr, d_B, d_L, consts) \longleftarrow ifun(args)$\label{alg.gen.call.ifun}\;
        $f \longleftarrow Evaluate(b_N, cfg, tr, d_B, d_L)$\label{alg.gen.eval}\;
        $scoredPop \longleftarrow (f, p) \cup scoredPop$\;
        $cinfo \longleftarrow consts \cup cinfo$\label{alg.gen.eval.end}\;
      }
      $combo \longleftarrow scoredPop \cup archive$\label{alg.gen.get.combo}\;
      $cross \longleftarrow Crossover(combo, rate_C)$\label{alg.gen.cross}\;
      $mut \longleftarrow Mutation(combo, cinfo, rate_M)$\label{alg.gen.mut}\;
      $pop \longleftarrow cross \cup mut$\label{alg.gen.new.pop}\;
      $archive \longleftarrow SortArchive(combo, size_A)$\label{alg.gen.new.archive}\;
      $(f^*, p^*) \longleftarrow head(archive)$\label{alg.gen.archive.head}\;
      $i \longleftarrow i + 1$\;
    }\label{alg.gen.loop.end}
    \Return{$(f^*, p^*)$}\label{alg.gen.return} 
  }
\end{algorithm}

The heart of our test data generation framework is in the \emph{Genetic Phase}. The main workflow of the underlying genetic algorithm (GA) is quite standard~\cite{poli2008field}, and with some adjustments is presented in Algorithm~\ref{alg.gen}. First, we read the \emph{config} file in line~\ref{alg.gen.read.config}. As a result, we get information about the number of elements in a population ($size_P$), size of the archive ($size_A$), number of generations ($size_G$) and respectively crossover ($rate_C$) and mutation ($rate_M$) rates. \emph{Archive} has the capacity of $size_A$ elements and stores the most fitted candidates observed so far. It is empty in the beginning of the evolution (line~\ref{alg.gen.arch.init}). The first population consisting of $size_P$ elements is randomly constructed from the elements in \emph{cinfo} (line~\ref{alg.gen.random.gen}). Inside of the loop (lines~\ref{alg.gen.loop.begin}-\ref{alg.gen.loop.end}) we are evolving the population until either the perfect fitness is found or the generation limit $size_G$ is reached. But first step in this loop is to score the current population~\ref{alg.gen.eval.begin}-\ref{alg.gen.eval.end}. Each candidate in the population has to be converted to an argument list by coercing it to a respective type according to the signature $sig$ (line~\ref{alg.gen.make.args}). Calling the instrumented function $ifun$ on those arguments (line~\ref{alg.gen.call.ifun}), we get 4-tuple consisting of the execution trace ($tr$), the branch distances ($d_B$), the loop distances ($d_L$) and the new set of constants ($consts$) collected at the run time. The next step is actually to evaluate the fitness value of the given candidate (line~\ref{alg.gen.eval}). Collected constants $consts$ are added to the existing constants info $cinfo$ (line~\ref{alg.gen.eval.end}). Eventually the scored population is combined with the archive (line~\ref{alg.gen.get.combo}) and is used for the crossover (line~\ref{alg.gen.cross}) and mutation steps (line~\ref{alg.gen.mut}). The rates specify the distribution in which the respective operations are applied to produce the new population (line~\ref{alg.gen.new.pop}). Scored population together with the current archive are sorted based on the fitness value, and the best $size_A$ elements form the new archive (line~\ref{alg.gen.new.archive}). On top of the archive we have the most fitted candidate observed over the course of all iterations (line~\ref{alg.gen.archive.head}). The fitness value of that element defines if perfect candidate is found (line~\ref{alg.gen.loop.end}) and it is return at the end of the algorithm (line~\ref{alg.gen.return}).

@@

Success of any search-based algorithm heavily depends on the choice of the fitness function (FF) that guides the search process. In our case FF is defined on CFG of the program.

\[
\mathcal{F}(n) = ...
\]

@@

\subsection{Static and Dynamic Analysis of JavaScript}
\label{sub.sec.js.static.anal}

@@

ACTARUS is a static taint analysis of JS\cite{guarnieri2011saving}.

Jalangi is dynamic analysis framework for JavaScript \cite{sen2013jalangi}.

Dynamic type inconsistency analysis (implemented on top Jalangi) for JavaScript\cite{pradel2015typedevil}.

Salable dynamic analysis framework for JS based on shadow executions~\cite{create_citation}.

Information-flow security for JS~\cite{hedin2012information}.

@@

Testing of AJAX application by means of crawling of the application to infer state-flow graph~\cite{mesbah2012crawling} ATUSA ~\cite{mesbah2012invariant}

Learning DOM invariants from multiple executions of the application~\cite{pattabiraman2010dodom}.

Measuring test adequacy for web application based on the DOM state coverage~\cite{mirzaaghaei2014dom}.

Combining human written test cases with the automatically generated once by crawling in order to extend test coverage~\cite{milani2014leveraging}.

DOM-aware JavaScript code completion~\cite{bajaj2014dompletion}.

\subsection{Formal Techniques}
\label{sub.sec.formal}

Modeling and reasoning about DOM events~\cite{lerner2012modeling}.

@@

JS unit test generation by means of symbolic execution~\cite{tanida2014automatic}.

Flycatcher~\cite{deautomatic}
